\huge ARuko and Editour: \\ \Large A Platform for Augmented Reality Tour Guide Apps

### 2019-10-03 paper.tex

>>>>

\section{NOxAR Assignment}
\label{sec:NOxAR}

On Monday, September 9th, Atticus approached us about an additional project he 
wanted us to tackle. He wanted us to adapt Kyoto VR's NOxAR app to use ground
plane detection. Currently, the NOxAR app is an AR app for Microsoft Hololens
that uses image targets with Vuforia. When viewing the correct image target,
the app projects a 3D model of a Noh Theater\footnote{A form of Japanese 
theater originating in the 14th century structured around song and slow 
dancing~\autocite{japanguide2018}.} performer dancing to background 
music~\autocite{noxar2018}. What Atticus wanted us to do was have the app use 
ground plane detection in order to display the Noh performer so that it could 
be displayed anywhere. Additionally, he wanted us to scale up the model so that
when displayed in AR, the performer would appear life-sized, as if she were 
really there dancing in the real world.

For this project, Atticus sent us the original Unity project files for NOxAR.
We then had to figure out how to turn the original project into a ground plane
AR app. At first we tried importing the assets for the Noh performer into a new
Unity project. We did this for a couple reasons. The first reason was because
we didn't want all of the extra components of the original NOxAR project to
get in the way of what we were trying to do. We also did this because the %could probably put an example pic here
original project was made with a 2017 version of Unity, so we wanted to try to
use our more recent version so we wouldn't risk running into any depricated 
features or functionalities. We did eventually get this method to work, but the
model of the Noh performer was lacking a lot of the details that the original 
model had. This was attributed to poor importation of the original assets, so 
we decided to try making changes to the original NOxAR project instead.

Per Atticus's advice, we deleted any and all unnecessary elements from the 
scene before proceeding. We also updated the Unity version of the project to
the 2019 version we were using, and updated the version of Vuforia to the most
recent version, neither of which created any problems. The process of getting
the model to appear on ground plane detection instead of image target 
recognition was relatively simple. We simply moved the model from an image 
target to a simulated ground plane, added a plane detector component to the
scene, and made sure the Vuforia settings were in place for ground plane
detection to work well. From there, we just had to test the app a few times so
we could properly scale the model to life size. So on Tuesday, September 17th, 
we completed the NOxAR ground plane adaptation to Atticus's saisfaction and
sent him the final APK file for the app.
